First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei

### 2017-05-25 eg6-letters/coherent/dvcs_he4_prl.tex

We acknowledge the staff of the Accelerator and Physics Divisions at Jefferson 
Lab for making this experiment possible. This work is supported by the U.S.  
Department of Energy, Office of Science, Office of Nuclear Physics, under 
contracts DE-AC02-06CH11357 and DE-AC05-06OR23177.

>>>>

We acknowledge the staff of the Accelerator and Physics Divisions at Jefferson 
Lab for making this experiment possible.

Dave Ireland- the United Kingdom's Science and Technology Facilities Council

Lamiaa- the Physics and Astronomy Department and the Office of Research and 
Economic Development at Mississippi State University, and the US Department of 
Energy Award DE-FG02-07ER41528.

- This work is supported by the U.S.  Department of Energy, Office of Science, 
Office of Nuclear Physics, under contracts DE-AC02-06CH11357 and 
DE-AC05-06OR23177.
